### 2013-06-18 latex/paper-PLOS_ONE-revised.tex
Redone Main Tables
Redid the tables. Found an error in MacCallum Correlations

\begin{center}
\begin{tabular}{lcccc}
Residue & Theoretical & Empirical & Miller \emph{et al.} (1987) & Rose \emph{et al.} (1985) \\
\hline Alanine & 129.0 & 121.0 & 113.0 & 118.1 \\
Arginine        & 274.0 & 265.0 & 241.0 & 256.0 \\
Asparagine    & 195.0 & 187.0 & 158.0 & 165.5 \\
Aspartate      & 193.0 & 184.0 & 151.0 & 158.7 \\
Cysteine        & 158.0 & 140.0 & 140.0 & 146.1 \\
Glutamate     & 223.0 & 215.0 & 183.0 & 186.2 \\
Glutamine      & 224.0 & 215.0 & 189.0 & 193.2  \\
Glycine          & 104.0 & 98.0 & 85.0 & 88.1  \\
Histidine        & 209.0 & 208.0 & 194.0 & 202.5  \\
Isoleucine     & 197.0 & 195.0 & 182.0 & 181.0  \\
Leucine         & 201.0 & 192.0 & 180.0 & 193.1  \\
Lysine           & 237.0 & 227.0 & 211.0 & 225.8  \\
Methionine   & 218.0 & 203.0 & 204.0 & 203.4  \\
Phenylalanine  & 239.0 & 228.0 & 218.0 & 222.8  \\
Proline & 159.0 & 159.0& 143.0 & 146.8  \\
Serine          & 151.0 & 143.0 & 122.0 & 129.8  \\
Threonine          & 172.0 & 161.0 & 146.0 & 152.5  \\
Tryptophan          & 282.0 & 265.0 & 259.0 & 266.3  \\
Tyrosine          & 263.0 & 255.0 & 229.0 & 236.8 \\
Valine          & 174.0 & 165.0 & 160.0 & 164.5  \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[H]
\caption{\label{tab:Corr}Absolute value of correlation coefficients $r$ between empirically derived and experimentally derived hydrophobicity scales. The largest correlation in each row is highlighted in bold.}
\begin{center}
\footnotesize
\begin{tabular}{lccccc}
 & \multicolumn{5}{c}{Empirical scale} \\ \cline{2-6}\\[-2ex]
Experimental scale & Mean RSA (Rose)$^\text{a}$ & Mean RSA (theor)$^\text{b}$ & Mean RSA (emp)$^\text{c}$ & 100\% buried$^\text{d}$ & 95\% buried$^\text{e}$\\
\hline
Wolfenden \emph{et al.}$^\text{f}$ & 0.614 & 0.699 & 0.687 & \textbf{0.830} & 0.786 \\
Kyte \& Doolittle$^\text{g}$ & 0.841 & 0.890 & 0.886 & \textbf{0.956} & \textbf{0.956} \\
Radzicka \& Wolfenden$^\text{h}$ & 0.804 & 0.860 & 0.857 & 0.848 & \textbf{0.896} \\
Moon \& Fleming$^\text{i}$ & 0.704 & 0.768 & 0.761 & 0.684 & \bf{0.777} \\
MacCallum \emph{et al.}$^\text{k}$ & 0.804 & 0.860 & 0.857 & 0.848 & \textbf{0.898} \\
Fauchere \& Pliska$^\text{l}$ & 0.904 & \textbf{0.911} & 0.910 & 0.734 & 0.882 \\
Wimley \emph{et al.}$^\text{m}$ & 0.430$^\dagger$ & 0.475 & \textbf{0.480} & 0.325$^\dagger$ & 0.425$^\dagger$ \\
\hline
\end{tabular}
\end{center}
{\footnotesize
\begin{raggedright}
$^\text{a}$Mean RSA of residues in protein structures, as calculated by Rose \emph{et al.}~\cite{Rose1985}.\\
$^\text{b}$Mean RSA of residues in protein structures, as given in column 2 of Table S2.\\ 
$^\text{c}$Mean RSA of residues in protein structures, as given in column 3 of Table S2.\\
$^\text{d}$Fraction of 100\% buried residues, as given in column 4 of Table S2.\\
$^\text{e}$Fraction of 95\% buried residues, as given in column 5 of Table S2.\\
$^\text{f}$Transfer energy from vapor to water~\cite{Wolfenden1981}.\\
$^\text{g}$Hybrid scale based on transfer energy from vapor to water and on the percentages of 95\% and 100\% buried residues in protein structures~\cite{Kyte1981}.\\
$^\text{h}$Transfer energy from cyclohexane to water~\cite{Radzicka1988}.\\
$^\text{i}$$\Delta\Delta G$ between the folded and unfolded state of a mutated membrane-inserted protein, outer membrane phospholipase~A~\cite{Moon2011}. \\
$^\text{k}$Transfer energy calculated from molecular-dynamic simulations of side-chain analogs within a bilayer~\cite{MacCallum2007}.\\
$^\text{l}$Transfer energy between octanol and water~\cite{Fauchere1983}.\\
$^\text{m}$Transfer energy of pentapeptides between octanol and water~\cite{Wimley1996}.\\
$^\dagger$Correlation not statistically significant; all other correlations are significant at $\alpha=0.05$.\\
\end{raggedright}
}
\end{table}

>>>>

\begin{center}
\begin{tabular}{lcccc}
Residue & Theoretical & Empirical & Miller \emph{et al.} (1987) & Rose \emph{et al.} (1985) \\
\hline Alanine & 128.0 & 121.0 & 113.0 & 118.1 \\
Arginine        & 272.0 & 265.0 & 241.0 & 256.0 \\
Asparagine    & 195.0 & 187.0 & 158.0 & 165.5 \\
Aspartate      & 192.0 & 187.0 & 151.0 & 158.7 \\
Cysteine        & 164.0 & 148.0 & 140.0 & 146.1 \\
Glutamate     & 221.0 & 214.0 & 183.0 & 186.2 \\
Glutamine      & 224.0 & 214.0 & 189.0 & 193.2  \\
Glycine          & 104.0 & 97.0 & 85.0 & 88.1  \\
Histidine        & 209.0 & 216.0 & 194.0 & 202.5  \\
Isoleucine     & 197.0 & 195.0 & 182.0 & 181.0  \\
Leucine         & 200.0 & 191.0 & 180.0 & 193.1  \\
Lysine           & 235.0 & 230.0 & 211.0 & 225.8  \\
Methionine   & 219.0 & 203.0 & 204.0 & 203.4  \\
Phenylalanine  & 237.0 & 228.0 & 218.0 & 222.8  \\
Proline & 159.0 & 154.0& 143.0 & 146.8  \\
Serine          & 153.0 & 143.0 & 122.0 & 129.8  \\
Threonine          & 171.0 & 163.0 & 146.0 & 152.5  \\
Tryptophan          & 284.0 & 264.0 & 259.0 & 266.3  \\
Tyrosine          & 263.0 & 255.0 & 229.0 & 236.8 \\
Valine          & 173.0 & 165.0 & 160.0 & 164.5  \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[H]
\caption{\label{tab:Corr}Absolute value of correlation coefficients $r$ between empirically derived and experimentally derived hydrophobicity scales. The largest correlation in each row is highlighted in bold.}
\begin{center}
\footnotesize
\begin{tabular}{lccccc}
 & \multicolumn{5}{c}{Empirical scale} \\ \cline{2-6}\\[-2ex]
Experimental scale & Mean RSA (Rose)$^\text{a}$ & Mean RSA (theor)$^\text{b}$ & Mean RSA (emp)$^\text{c}$ & 100\% buried$^\text{d}$ & 95\% buried$^\text{e}$\\
\hline
Wolfenden \emph{et al.}$^\text{f}$ & 0.614 & 0.693 & 0.681 & \textbf{0.827} & 0.775 \\
Kyte \& Doolittle$^\text{g}$ & 0.841 & 0.884 & 0.881 & \textbf{0.953} & 0.948 \\
Radzicka \& Wolfenden$^\text{h}$ & 0.804 & 0.856 & 0.851 & 0.844 & \textbf{0.887} \\
Moon \& Fleming$^\text{i}$ & 0.704 & 0.761 & 0.752 & 0.678 & \bf{0.766} \\
Fauchere \& Pliska$^\text{l}$ & 0.904 & \textbf{0.908} & 0.910 & 0.734 & 0.878 \\
Wimley \emph{et al.}$^\text{m}$ & 0.430$^\dagger$ & 0.466 & \textbf{0.472} & 0.323$^\dagger$ & 0.416$^\dagger$ \\
MacCallum \emph{et al.}$^\text{k}$ & \textbf{0.318}$^\dagger$ & 0.268$^\dagger$ & 0.285$^\dagger$ & 0.116$^\dagger$ & 0.227$^\dagger$ \\
\hline
\end{tabular}
\end{center}
{\footnotesize
\begin{raggedright}
$^\text{a}$Mean RSA of residues in protein structures, as calculated by Rose \emph{et al.}~\cite{Rose1985}.\\
$^\text{b}$Mean RSA of residues in protein structures, as given in column 2 of Table S2.\\ 
$^\text{c}$Mean RSA of residues in protein structures, as given in column 3 of Table S2.\\
$^\text{d}$Fraction of 100\% buried residues, as given in column 4 of Table S2.\\
$^\text{e}$Fraction of 95\% buried residues, as given in column 5 of Table S2.\\
$^\text{f}$Transfer energy from vapor to water~\cite{Wolfenden1981}.\\
$^\text{g}$Hybrid scale based on transfer energy from vapor to water and on the percentages of 95\% and 100\% buried residues in protein structures~\cite{Kyte1981}.\\
$^\text{h}$Transfer energy from cyclohexane to water~\cite{Radzicka1988}.\\
$^\text{i}$$\Delta\Delta G$ between the folded and unfolded state of a mutated membrane-inserted protein, outer membrane phospholipase~A~\cite{Moon2011}. \\
$^\text{k}$Transfer energy calculated from molecular-dynamic simulations of side-chain analogs within a bilayer~\cite{MacCallum2007}.\\
$^\text{l}$Transfer energy between octanol and water~\cite{Fauchere1983}.\\
$^\text{m}$Transfer energy of pentapeptides between octanol and water~\cite{Wimley1996}.\\
$^\dagger$Correlation not statistically significant; all other correlations are significant at $\alpha=0.05$.\\
\end{raggedright}
}
\end{table}
